---
title: "Homework4"
author: "Yeabin"
date: "2022-09-24"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<h2> Homework 4 </h2>

Make sure that the following two packages are installed.
```{r}

library(tidyverse)
library(ggthemes)
library(ggrepel)

```

We will use two data set county_map and county_data for this homework 

### Part I

We merge the two data frames using the shared FIPS id column:
```{r}
load('county_map.rda')
load('county_data.rda')
county_full <- left_join(county_map, county_data, by = "id")
```

Let’s draw two new county-level maps. Look at the column su_gun6. It is about firearm-related suicides per 100,000 population, 1999-2015. This type of data is called factor variable, cut into six categories. We also have a pop_dens6 variable that divides the population density into six categories.

#### Question 1
Draw a county-level map using su_gun6 variable. Make sure that you must use: 
```
geom_polygon(size = 0.04)
coord_equal()
scale_fill_brewer(palette="Reds")
theme_map() 
```
```{r}
p0 <- ggplot(data = county_full,
            aes(x = long, y =lat, group =group, fill=su_gun6))

p0 + geom_polygon(color = "gray90", size = 0.04)+
  coord_equal()+
  scale_fill_brewer(palette='Reds')+
  theme_map()
 
```
- What's the role of 4 functions above?
- Improve the texts using labs(title = , fill = ) and theme(legend.position = ) 
```{r}
#geom_polygon a geometry function that make sure start and end points are connected inside the graph,in which group function are connected  together.
#coord_equal() make sure that x and y axis has the same scale 
#scale_fill_brewer(palette="Reds") provides sequential, diverging, qualitative color schemes, palette provides different selection of palette 
#theme_map() uses themes to display maps from geom_map()function

```

```{r}
p0 <- ggplot(data = county_full,
            aes(x = long, y =lat, group =group, fill=su_gun6))

p0 + geom_polygon(color = "gray90", size = 0.04)+
  coord_equal()+
  scale_fill_brewer(palette='Reds')+
  theme_map()+
  labs(title ='country data map', fill ='firearm-related suicides per 100,000 population' )+
  theme(legend.position ='top' )

```

#### Question 2
Draw a county-level map using pop_dens6 variable using the same functions above.
```{r}
p1 <- ggplot(data = county_full,
            aes(x = long, y =lat, group =group, fill=pop_dens6))

p1 + geom_polygon(color = "gray90", size = 0.04)+
  coord_equal()+
  scale_fill_brewer(palette='Reds')+
  theme_map()+
  labs(title ='country data map', fill ='population density divided into 6' )+
  theme(legend.position ='bottom' )


```
#### Question 3
What's your interpretation regarding these two figures? (~ 200 words)
```{r}
# For the first figure, according to the category representation, we can see more frequency occurrence of fire alarm related suicide incident happen that concentrated on the West coast, as the color density is the heaviest in most of the West Coast states compare to the central. East coast has less severe representation compared to West Coast.If you look closer, you can find the scale around states like AK, TX(central, south America) is smaller than the West, meaning the color differences among are more obvious. When I check the summary(county_full) I found that certain states have more records than the others, such as TX/AK has more, there more there are more color mapping differences.
# For the second figure. Since the mapping represents the population density divided into 6, the scale is larger than figure one as it records not only the suicide population but population in general. From the result. There is lower population density on the West coast states compare to the rest of the states even though states roughly around CA has highest population density. Unlike figure 1, East Coast, central States have higher population concentration as well as states around FL. 

```

#### Question 4
Revisit <em>Flipped counties, 2016</em> figures in lecture 9.
```{r}
setwd("~/Documents/ibs_course/BUS240/data")
load("county_data.rda")
party_colors <- c("#2E74C0", "#CB454A") # Democrat Blue and Republican Red
p0 <- ggplot(data = subset(county_data,
                           flipped == "No"),
             mapping = aes(x = pop,
                           y = black/100))
p1 <- p0 + geom_point(alpha = 0.15, color = "gray50") + scale_x_log10(labels=scales::comma) 
p2 <- p1 + geom_point(data = subset(county_data,
                                    flipped == "Yes"),
                      mapping = aes(x = pop, y = black/100,
                                    color = partywinner16)) +
  scale_color_manual(values = party_colors)
p3 <- p2 + scale_y_continuous(labels=scales::percent) +
    labs(color = "County flipped to ... ",
         x = "County Population (log scale)",
         y = "Percent Black Population",
         title = "Flipped counties, 2016",
         caption = "Counties in gray did not flip.")
p4 <- p3 + geom_text_repel(data = subset(county_data,
                                      flipped == "Yes" &
                                      black  > 25),
                           mapping = aes(x = pop,
                                   y = black/100,
                                   label = county), size = 2)
p4
```

For this exercise, 

1. create the scatter plot with the counties in which the number of population having less than 75 % of data points (the third quartile) only
2. use the partisan colors to show the counties flipped
3. plot the text labels for the counties flipped to Democrat 
  - the text label needs to address both county and state: suffolk county, MA
  
```{r}
poppercentile <- quantile(county_data$pop, probs = c(.75)) #use county_data as numeric vector to find 75% percentile, stored in pop percentile
newpop<-county_data %>% 
  filter(pop <= poppercentile)
#filter number of population having less than 75% of data points in newpop as new dataframe

party_colors <- c("#2E74C0", "#CB454A")
p0 <- ggplot(data = subset(newpop,
                           flipped == "No"),
             mapping = aes(x = pop,
                           y = black/100))
p1 <- p0 + geom_point(alpha = 0.15, color = "gray50") + scale_x_log10(labels=scales::comma) 
p2 <- p1 + geom_point(data = subset(newpop,
                                    flipped == "Yes"),
                      mapping = aes(x = pop, y = black/100,
                                    color = partywinner16)) +
  scale_color_manual(values = party_colors)
p3 <- p2 + scale_y_continuous(labels=scales::percent) +
    labs(color = "County flipped to ... ",
         x = "County Population (log scale)",
         y = "Percent Black Population",
         title = "Flipped counties, 2016",
         caption = "Counties in gray did not flip.")
p4 <- p3 + geom_text_repel(data = subset(newpop,
                                      flipped == "Yes" & 
                                      black  > 25),
                           mapping = aes(x = pop,
                                   y = black/100,
                                   label = state), size = 2)
p4

```


```{r}

p0 <- ggplot(data = subset(newpop,
                           flipped == "No" ),
             mapping = aes(x = pop,
                           y = black/100))
p1 <- p0 + geom_point(alpha = 0.15, color = "gray50") + scale_x_log10(labels=scales::comma) 
p2 <- p1 + geom_point(data = subset(newpop,
                                    flipped == "Yes" ),
                      mapping = aes(x = pop, y = black/100,
                                    color = partywinner16)) +
  scale_color_manual(values = party_colors)
p3 <- p2 + scale_y_continuous(labels=scales::percent) +
    labs(color = "County flipped to ... ",
         x = "County Population (log scale)",
         y = "Percent Black Population",
         title = "Flipped counties, 2016",
         caption = "Counties in gray did not flip.")
p4 <- p3 + geom_text_repel(data = subset(county_data,
                                      flipped == "Yes" &
                                      black  > 25),
                           mapping = aes(x = pop,
                                   y = black/100,
                                   label = paste(name, ", ", state)), size = 2) #using paste function to concatenate strings of county names and state names
p4
```
```
